---
title: "TeviHub"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: readable
    logo: images/SWEEPLOGO.png
---
<script>
$('.navbar-logo').wrap('<a href="http://www.sweep.ac.uk"> target=_blank');
</script>

```{r, setup, include=FALSE}
##### TO render whole site run line command:
#   rmarkdown::render_site()
#   https://jrmosedale.github.io/dashboard/

# Linking multiple Rmd files - usew either bookdown or child files - reF:https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output

#  devtools::install_github("walkerke/bsselectR")

library(flexdashboard)
library(bsselectR)
library(raster)
library(leaflet)
library(magrittr)
library(colorspace)
library(rgeos)
library(ggplot2)
library(rgdal)
library(sf)
library(units)
library(leaflet.extras)
library(htmlwidgets)
library(zonator)
library(RColorBrewer)
library(DT)

#### iframe refs: https://stackoverflow.com/questions/15255858/set-the-iframe-height-automatically
### https://stackoverflow.com/questions/44371799/how-can-i-insert-html-widget-objects-leaflet-map-or-html-table-in-an-html-mark

################################################
# Directories
###############################################
# if (Sys.getenv("HOME")=="/Users/jm622") in.root<-paste0(Sys.getenv("HOME"),"/OneDrive - University of Exeter/Rprojects/EG4B/app/")
in.root<-"data/"
dir_cna<-paste0(in.root,"cnamaps/")
#dir_ZProject<-paste0("/Volumes/Pocket_Sam/data/Zonation_Projects/Cornwall_Priority/")
#dir_zinputs<-"/Volumes/Pocket_Sam/data/Zonation_data/"

################################################
# Load functions 
###############################################
source("Rscripts/functions.R")

# Presentation functions etc
csa_icons <- function() {
  awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = "green")
}

cta_icons<- function() {
  awesomeIcons(
    icon = 'ios-close',
    iconColor = 'black',
    library = 'ion',
    markerColor = "blue"
  )
}

tevi_icons <- function(tevibus){
  awesomeIcons(
    icon = tevibus$Icon,
    iconColor = 'black',
    library = 'fa',
    markerColor = tevibus$Colour
  )
}

zero_to_NA<-function(r){
  result<-calc(r,fun=function(x){ifelse(x==0,NA,x)})
  return(result)
}

# Recalculating rank after masking
rank_after_mask<-function(r,msk){
  msk.cells<-getValues(mask(r,msk))
  min.prot<-min(msk.cells,na.rm=TRUE)
  # num.prot<-length(msk.cells[-which(is.na(msk.cells))])
  rem.cells<-getValues(mask(r,msk,inverse=TRUE))
  max.rem<-max(rem.cells,na.rm=TRUE)
  new.ranks<-(rem.cells/max.rem)*1
  new.r<-setValues(r,new.ranks)
  return(new.r)
}

```

A. Business Engagement 
============================================================================================
Businesses participating (as of September 2018) in the [Tevi](https://tevi.co.uk) programme, award winners of the [Cornwall Sustainability Awards](https://www.cornwallsustainabilityawards.org) (2004-17) and [Cornwall Tourism Awards](http://www.cornwalltourismawards.org.uk) (2018 only).
Click on marker for further information.



Column {.tabset}
------------------------------------------------------------------------------------------------------------
### Map 1 Tevi Businesses

```{r,context='data', include=FALSE}

############################################
# LOAD Business data and prepare for mapping
############################################

# Business data
tevibus<- st_read(paste0(in.root,"tevibus.shp"))
csawinners<-st_read(paste(in.root,"csawinners.shp",sep=""))
cta2018<- st_read(paste0(in.root,"cta2018.shp"))
st_crs(tevibus)<-st_crs(27700)
st_crs(csawinners)<-st_crs(27700)
st_crs(cta2018)<-st_crs(27700)

```


```{r,echo=FALSE,out.width='100%', fig.align='center'}

# Create popup message
tevi.popup<-paste("<b>",tevibus$Enterprise,"</b>","<br>","Sector: ",tevibus$Sector,"<br>","Tevi Status: ",tevibus$Status,"<br>") 

teviplot<- prepare_sf_for_leaflet(tevibus)

leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addAwesomeMarkers(data=teviplot,
                    icon=tevi_icons(teviplot),  
                    label = ~as.character(Enterprise),
                    popup = tevi.popup
)


```

### Map 2 Cornwall Sustainability and Tourism Award Winners

```{r,  echo=FALSE}
# Create popup message
csa.popup<-paste("<b>",csawinners$Business,"</b>","-",csawinners$Award,csawinners$Year)
cta.popup<-paste("<b>",cta2018$Enterprise,"</b>","-",cta2018$Award,cta2018$Year)


leaflet() %>% 
setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
addProviderTiles("OpenStreetMap.Mapnik") %>%
addScaleBar() %>%
addAwesomeMarkers(data=prepare_sf_for_leaflet(csawinners),
                  icon=csa_icons(), 
                  label = ~as.character(Business),
                  popup = csa.popup,
                  group= "CSA businesses")  %>%
addAwesomeMarkers(data=prepare_sf_for_leaflet(cta2018),
                  icon=cta_icons(), 
                  label = ~as.character(Enterprise),
                  popup = cta.popup,
                  group ="CTA businesses" )  %>%
addLayersControl(
                  overlayGroups =c("CSA businesses", "CTA businesses"),
                  options = layersControlOptions(collapsed=FALSE)  
)  %>%
hideGroup(c("CTA businesses"))


```

B. Ecosystem Services 
============================================================================================
Important: The habitats and estimates of key ecosystem services presented here are calculated on the basis of 2015 landcover data.

Column {.tabset}
------------------------------------------------------------------------------------------------------------

### Maps of Services
```{r,context='data', include=FALSE}

# Load service rasters and determine palette for each

# Soil loss mitigation
soilmitig.r<-raster(paste0(in.root,"ecoservices/ecoservice_soillossmitig.tif"))
crs(soilmitig.r)<- CRS('+init=EPSG:27700')
soilmitig.vals<-getValues(soilmitig.r)

# Aboveground carbon 
abovecarbon.r<-raster(paste0(in.root,"ecoservices/ecoservice_aboveground_carbon.tif"))
crs(abovecarbon.r)<- CRS('+init=EPSG:27700')
abovecarbon.vals<-getValues(abovecarbon.r)

# Pollination 
pollination.r<-raster(paste0(in.root,"ecoservices/ecoservice_pollination.tif"))
crs(pollination.r)<- CRS('+init=EPSG:27700')
pollination.vals<-getValues(pollination.r)

# Flood mitigation
floodmitig.r<-raster(paste0(in.root,"ecoservices/ecoservice_floodmitig.tif"))
crs(floodmitig.r)<- CRS('+init=EPSG:27700')
floodmitig.vals<-getValues(floodmitig.r)

# Drinking water quality
drinkqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_drinkwater.tif"))
crs(drinkqual.r)<- CRS('+init=EPSG:27700')
drinkqual.vals<-getValues(drinkqual.r)

# Aquaculture water quality
aquaqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_aquaculture.tif"))
crs(aquaqual.r)<- CRS('+init=EPSG:27700')
aquaqual.vals<-getValues(aquaqual.r)

# Bathing water quality 
bathqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_bathingwater.tif"))
crs(bathqual.r)<- CRS('+init=EPSG:27700')
bathqual.vals<-getValues(bathqual.r)

# Not good catchments water quality 
catchqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_catchmentquality.tif"))
crs(catchqual.r)<- CRS('+init=EPSG:27700')
catchqual.vals<-getValues(catchqual.r)

#servicepal<-colorBin("Greens", domain = NULL, bins = 7, na.color = "transparent")
servicepal<-colorNumeric("YlOrRd", domain = NULL,  na.color = "transparent")

```

```{r,  echo=FALSE}

leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addRasterImage(abovecarbon.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Aboveground_carbon") %>%
  addRasterImage(pollination.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Pollination") %>%
  addRasterImage(soilmitig.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Soil_loss_mitigation") %>%
  addRasterImage(floodmitig.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Flood_mitigation") %>%
  addRasterImage(drinkqual.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Drinking_water") %>%
  addRasterImage(aquaqual.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Aquaculture") %>%
  addRasterImage(bathqual.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Bathing_water") %>%
  addLegend(position = "bottomright",
            pal=servicepal, values=0:100,opacity=1) %>%

  addLayersControl(
    baseGroups =c("Aboveground_carbon","Pollination","Soil_loss_mitigation",
                     "Flood_mitigation","Drinking_water","Aquaculture","Bathing_water"),
    options = layersControlOptions(collapsed=FALSE)  )  %>%
  
  hideGroup(c("Pollination","Soil_loss_mitigation",
             "Flood_mitigation","Drinking_water","Aquaculture","Bathing_water"))

```


C. Nature network mapping 
============================================================================================

Column {.tabset}
------------------------------------------------------------------------------------------------------------

### Nature network map     
Prioritization of 'non-protected' areas according to estimates of their current biodiversity, connectivity and ecosystem services. Areas currently benefiting from SSSI, SAC, SPA, national or local natures reserves are excluded from ranking. The top twenty percent most highly ranked/valued areas are shown in three bands: Band1 = top 5%, Band 2=  5-10%, Band 3=  10-20%. Resolution = 100m2. Click top right icon on map to select layers.    
```{r, echo=FALSE}

prot.map1.filername<-paste0("maps/","protect/map_v25.html")

htmltools::tags$iframe(src = prot.map1.filername, frameborder="0", style="overflow: hidden; height: 90%; width: 100%; position: absolute;")
```


### Method notes
```{r,echo=FALSE }

natnetwork.doc<-paste0("documentation/","Prioritization_maps_documentation_webversion.htm")

htmltools::tags$iframe(src = natnetwork.doc, frameborder="0", style="overflow: hidden; height: 100%; width: 80%; position: absolute;")
```

   
D. Opportunity mapping 
============================================================================================

Column {.tabset}
------------------------------------------------------------------------------------------------------------

```{r,context='data', include=FALSE}
woodopp.data.df<-read.csv("data/documentation/woodland_data_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 

```

### Woodland opportunity map
Prioritization of woodland creation opportunities on the basis of estimates of biodiversity and ecosystem services benefits Most highly ranked/valued oppoortunity areas are shown in three bands: Band1 = 50% increase in woodland cover, Band 1 & 2 =  doubling in woodland cover, Band 1,2 & 3 =  tripling in woodland cover. Resolution = 100m2. Click top right icon on map to select layers.

```{r, echo=FALSE}

opp.map1.filername<-paste0("maps/","opps/opp_woodland_map_v14.html")

htmltools::tags$iframe(src = opp.map1.filername, frameborder="0", style="overflow: hidden; height: 90%; width: 100%; position: absolute;")

```

### Method Notes
```{r child = 'PRIORITYMAP_2.Rmd'}

# woodopp.method<-paste0("documentation/","Woodland creation test.html")
# htmltools::tags$iframe(src = woodopp.method, frameborder="0", style="overflow: hidden; height: 100%; width: 100%; position: absolute;")

```

### Data Sources
```{r, echo=FALSE}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.data.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.data.df)),
          rownames=FALSE,colnames = c('Type of Factor','Factor','Key Data Source','Use in Map','Notes'))

```


D. Area maps
============================================================================================
This section is currently UNDER DEVELOPMENT

Column {.tabset}
------------------------------------------------------------------------------------------------------------

### Community Network Areas

```{r,context='data', include=FALSE}
############################################
# LOAD Parish areas
############################################


############################################
# LOAD Community network areas
############################################

# Create list of files names
cna.shp<-st_read(paste0(in.root,"community_network_areas.shp"))
st_crs(cna.shp)<-st_crs(27700)
cna.shp<-st_transform(cna.shp,4326)
cna.names<-paste0(cna.shp$NAME)
cna.names<-sort(cna.names)

cna.list<-list.files("maps/")
cna.list<-sort(cna.list)
cna.list<-paste0("maps/",cna.list)
names(cna.list)<-cna.names

```

```{r,  echo=FALSE}

bsselect(cna.list, type = "iframe")

```


### Parishes


### Catchments


### Explanatory notes
Some sort of explanation and/or legend could be placed here, perhaps including links to a methodology document etc?


