---
title: "TeviHub"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: readable
    logo: images/SWEEPLOGO.png
---
<script>
$('.navbar-logo').wrap('<a href="http://www.sweep.ac.uk"> target=_blank');
</script>

```{r, setup, include=FALSE}
##### TO render whole site run line command:
#   rmarkdown::render_site()
#   https://jrmosedale.github.io/dashboard/

# Linking multiple Rmd files - usew either bookdown or child files - reF:https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output

#  devtools::install_github("walkerke/bsselectR")

library(flexdashboard)
library(bsselectR)
library(raster)
library(leaflet)
library(magrittr)
library(colorspace)
library(rgeos)
library(ggplot2)
library(rgdal)
library(sf)
library(units)
library(leaflet.extras)
library(htmlwidgets)
library(zonator)
library(RColorBrewer)
library(DT)

#### iframe refs: https://stackoverflow.com/questions/15255858/set-the-iframe-height-automatically
### https://stackoverflow.com/questions/44371799/how-can-i-insert-html-widget-objects-leaflet-map-or-html-table-in-an-html-mark

################################################
# Directories
###############################################
# if (Sys.getenv("HOME")=="/Users/jm622") in.root<-paste0(Sys.getenv("HOME"),"/OneDrive - University of Exeter/Rprojects/EG4B/app/")
in.root<-"data/"
dir_cna<-paste0(in.root,"cnamaps/")
dir_ZProject<-paste0("/Volumes/Pocket_Sam/data/Zonation_Projects/Cornwall_Priority/")
dir_zinputs<-"/Volumes/Pocket_Sam/data/Zonation_data/"

################################################
# Load functions 
###############################################
source("Rscripts/functions.R")

# Presentation functions etc
csa_icons <- function() {
  awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = "green")
}

cta_icons<- function() {
  awesomeIcons(
    icon = 'ios-close',
    iconColor = 'black',
    library = 'ion',
    markerColor = "blue"
  )
}

tevi_icons <- function(tevibus){
  awesomeIcons(
    icon = tevibus$Icon,
    iconColor = 'black',
    library = 'fa',
    markerColor = tevibus$Colour
  )
}

zero_to_NA<-function(r){
  result<-calc(r,fun=function(x){ifelse(x==0,NA,x)})
  return(result)
}

# Recalculating rank after masking
rank_after_mask<-function(r,msk){
  msk.cells<-getValues(mask(r,msk))
  min.prot<-min(msk.cells,na.rm=TRUE)
  # num.prot<-length(msk.cells[-which(is.na(msk.cells))])
  rem.cells<-getValues(mask(r,msk,inverse=TRUE))
  max.rem<-max(rem.cells,na.rm=TRUE)
  new.ranks<-(rem.cells/max.rem)*1
  new.r<-setValues(r,new.ranks)
  return(new.r)
}

```

A. Business Locations and Engagement 
============================================================================================
Businesses participating (as of September 2018) in the [Tevi](https://tevi.co.uk) programme, award winners of the [Cornwall Sustainability Awards](https://www.cornwallsustainabilityawards.org) (2004-17) and [Cornwall Tourism Awards](http://www.cornwalltourismawards.org.uk) (2018 only).
Click on marker for further information.



Column {.tabset}
------------------------------------------------------------------------------------------------------------
### Map 1 Tevi Businesses

```{r,context='data', include=FALSE}

############################################
# LOAD Business data and prepare for mapping
############################################

# Business data
tevibus<- st_read(paste0(in.root,"tevibus.shp"))
csawinners<-st_read(paste(in.root,"csawinners.shp",sep=""))
cta2018<- st_read(paste0(in.root,"cta2018.shp"))
st_crs(tevibus)<-st_crs(27700)
st_crs(csawinners)<-st_crs(27700)
st_crs(cta2018)<-st_crs(27700)

```


```{r,echo=FALSE,out.width='100%', fig.align='center'}

# Create popup message
tevi.popup<-paste("<b>",tevibus$Enterprise,"</b>","<br>","Sector: ",tevibus$Sector,"<br>","Tevi Status: ",tevibus$Status,"<br>") 

teviplot<- prepare_sf_for_leaflet(tevibus)

leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addAwesomeMarkers(data=teviplot,
                    icon=tevi_icons(teviplot),  
                    label = ~as.character(Enterprise),
                    popup = tevi.popup
)


```

### Map 2 Cornwall Sustainability and Tourism Award Winners

```{r,  echo=FALSE}
# Create popup message
csa.popup<-paste("<b>",csawinners$Business,"</b>","-",csawinners$Award,csawinners$Year)
cta.popup<-paste("<b>",cta2018$Enterprise,"</b>","-",cta2018$Award,cta2018$Year)


leaflet() %>% 
setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
addProviderTiles("OpenStreetMap.Mapnik") %>%
addScaleBar() %>%
addAwesomeMarkers(data=prepare_sf_for_leaflet(csawinners),
                  icon=csa_icons(), 
                  label = ~as.character(Business),
                  popup = csa.popup,
                  group= "CSA businesses")  %>%
addAwesomeMarkers(data=prepare_sf_for_leaflet(cta2018),
                  icon=cta_icons(), 
                  label = ~as.character(Enterprise),
                  popup = cta.popup,
                  group ="CTA businesses" )  %>%
addLayersControl(
                  overlayGroups =c("CSA businesses", "CTA businesses"),
                  options = layersControlOptions(collapsed=FALSE)  
)  %>%
hideGroup(c("CTA businesses"))


```

B. Habitats & Ecosystem Services 
============================================================================================

Column {.tabset}
------------------------------------------------------------------------------------------------------------
### Map 1 Habitats
```{r,context='data', include=FALSE}

############################################
# LOAD Habitat and Service data and prepare for mapping
############################################

# Landcover data
landcover.r<-raster(paste0(in.root,"domcover.tif"))
urban.r<-calc(landcover.r,fun=function(x){ifelse(x>19,1,NA)})
arable.r<-calc(landcover.r,fun=function(x){ifelse(x==3,1,NA)})
improvgrass.r<-calc(landcover.r,fun=function(x){ifelse(x==4,1,NA)})

# Priority habitats
priority.r<-zero_to_NA(raster(paste0(in.root,"priority_habitat.tif")))

# Protected areas
#protected.r<-
#st_crs(protected.r)<-st_crs(27700)


```


```{r,  echo=FALSE}
leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addRasterImage(urban.r,color="black", 
               opacity = 0.7,project=TRUE,group="Urban") %>%
  addRasterImage(arable.r,color="brown", 
                 opacity = 0.7,project=TRUE,group="Arable") %>%
  addRasterImage(improvgrass.r,color="green", 
                 opacity = 0.7,project=TRUE,group="Improved_Grass") %>%
  addRasterImage(priority.r,color="purple", 
                 opacity = 0.7,project=TRUE,group="Priority_habitats") %>%
  # addRasterImage(protected.r,color="yellow", 
  #               opacity = 0.7,project=TRUE,group="Protected_areas") %>%
  addLayersControl(
    overlayGroups =c("Urban", "Arable","Improved_Grass","Priority_habitats","Protected_areas"),
    options = layersControlOptions(collapsed=FALSE)  ) %>%
  hideGroup(c("Arable","Improved_Grass","Priority_habitats","Protected_areas"))
```

### Map 2 Services
Key ecosystem service and associated layers are detailed below.
```{r,context='data', include=FALSE}

# Load service rasters and determine palette for each

# Soil loss mitigation
soilmitig.r<-raster(paste0(in.root,"ecoservices/ecoservice_soillossmitig.tif"))
crs(soilmitig.r)<- CRS('+init=EPSG:27700')
soilmitig.vals<-getValues(soilmitig.r)
soilmitig.pal<-mapcolour("soilmitig",soilmitig.vals)

# Aboveground carbon 
abovecarbon.r<-raster(paste0(in.root,"ecoservices/ecoservice_aboveground_carbon.tif"))
crs(abovecarbon.r)<- CRS('+init=EPSG:27700')
abovecarbon.vals<-getValues(abovecarbon.r)
abovecarbon.pal<-mapcolour("abovecarbon",abovecarbon.vals)

# Pollination 
pollination.r<-raster(paste0(in.root,"ecoservices/ecoservice_pollination.tif"))
crs(pollination.r)<- CRS('+init=EPSG:27700')
pollination.vals<-getValues(pollination.r)
pollination.pal<-mapcolour("abovecarbon",pollination.vals)

# Flood mitigation
floodmitig.r<-raster(paste0(in.root,"ecoservices/ecoservice_floodmitig.tif"))
crs(floodmitig.r)<- CRS('+init=EPSG:27700')
floodmitig.vals<-getValues(floodmitig.r)
floodmitig.pal<-mapcolour("floodmitig",floodmitig.vals)

# Drinking water quality
drinkqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_drinkwater.tif"))
crs(drinkqual.r)<- CRS('+init=EPSG:27700')
drinkqual.vals<-getValues(drinkqual.r)
drinkqual.pal<-mapcolour("drinkqual",drinkqual.vals)

# Aquaculture water quality
aquaqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_aquaculture.tif"))
crs(aquaqual.r)<- CRS('+init=EPSG:27700')
aquaqual.vals<-getValues(aquaqual.r)
aquaqual.pal<-mapcolour("aquaqual",aquaqual.vals)

# Bathing water quality 
bathqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_bathingwater.tif"))
crs(bathqual.r)<- CRS('+init=EPSG:27700')
bathqual.vals<-getValues(bathqual.r)
bathqual.pal<-mapcolour("bathqual",bathqual.vals)

# Not good catchments water quality 
catchqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_catchment_quality.tif"))
crs(catchqual.r)<- CRS('+init=EPSG:27700')
catchqual.vals<-getValues(catchqual.r)
bathqual.pal<-mapcolour("bathqual",catchqual.vals)

```

```{r,  echo=FALSE}

leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addRasterImage(abovecarbon.r, colors=abovecarbon.pal,
               opacity = 0.8,project=TRUE, group="Aboveground_carbon") %>%
  addRasterImage(pollination.r, colors=pollination.pal,
               opacity = 0.8,project=TRUE, group="Pollination") %>%
  addRasterImage(soilmitig.r, colors=soilmitig.pal,
               opacity = 0.8,project=TRUE, group="Soil_loss_mitigation") %>%
  addRasterImage(floodmitig.r, colors=floodmitig.pal,
               opacity = 0.8,project=TRUE, group="Flood_mitigation") %>%
  addRasterImage(drinkqual.r, colors=drinkqual.pal,
               opacity = 0.8,project=TRUE, group="Drinking_water") %>%
  addRasterImage(aquaqual.r, colors=aquaqual.pal,
               opacity = 0.8,project=TRUE, group="Aquaculture") %>%
  addRasterImage(bathqual.r, colors=bathqual.pal,
               opacity = 0.8,project=TRUE, group="Bathing_water") %>%

   addLegend(position = "bottomright",
            pal=abovecarbon.pal, values=abovecarbon.vals,
            group="Aboveground_carbon", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=pollination.pal, values=pollination.vals,
            group="Pollination", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=soilmitig.pal, values=soilmitig.vals,
            group="Soil_loss_mitigation", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=floodmitig.pal, values=floodmitig.vals,
            group="Flood_mitigation", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=drinkqual.pal, values=drinkqual.vals,
            group="Drinking_water", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=aquaqual.pal, values=aquaqual.vals,
            group="Aquaculture", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=bathqual.pal, values=bathqual.vals,
            group="Bathing_water", opacity=1) %>%
  
  addLayersControl(
    overlayGroups =c("Aboveground_carbon","Pollination","Soil_loss_mitigation",
                     "Flood_mitigation","Drinking_water","Aquaculture","Bathing_water"),
    options = layersControlOptions(collapsed=FALSE)  )  %>%
  
  hideGroup(c("Pollination","Soil_loss_mitigation",
             "Flood_mitigation","Drinking_water","Aquaculture","Bathing_water"))

```


### Explanatory notes
Some sort of explanation and/or legend could be placed here, perhaps including links to a methodology document etc?


C. Prioritization mapping 
============================================================================================
Column {.tabset}
------------------------------------------------------------------------------------------------------------
### Nature network mapping

```{r, echo=FALSE}

prot.map1.filername<-paste0("maps/","opps/protect_map_vv18.html")

htmltools::tags$iframe(src = prot.map1.filername, frameborder="0", style="overflow: hidden; height: 100%; width: 100%; position: absolute;")
```

### Nature network - Method notes
```{r child = 'PRIORITYMAP_1.Rmd'}
```

   
D. Opportunity mapping 
============================================================================================

Column {.tabset}
------------------------------------------------------------------------------------------------------------

```{r,context='data', include=FALSE}
woodopp.exclude.df<-read.csv("data/documentation/woodland_exclusion_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 
woodopp.constrain.df<-read.csv("data/documentation/woodland_constraint_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 
woodopp.facilitate.df<-read.csv("data/documentation/woodland_facilitate_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 
woodopp.benefit.df<-read.csv("data/documentation/woodland_benefit_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 


```

### Woodland opportunity map

```{r, echo=FALSE}
#opp.map1.filername<-paste0("maps/","opps/opp_woodland_map_v08.html")
#opp.map1.filername<-paste0("maps/","opps/opp_woodland_map_v07.html")

opp.map1.filername<-paste0("maps/","opps/opp_woodland_map_vv09.html")

htmltools::tags$iframe(src = opp.map1.filername, frameborder="0", style="overflow: hidden; height: 100%; width: 100%; position: absolute;")

```

### Method and Approach
i.	Identify all areas not to consider for woodland creation but which should be preserved to be included in connectivity benefits (ie existing woodland, priority habitats).  
ii.	Treat all remaining areas as potential woodland creation areas.  
iii. Identify "contrainst" to habitat creation and realisation of benefits. Apply negative weighting for likely constraints on opportunity (built up areas, High grade agricultural land, topographical constraints).   
iv.	Calculate “benefits” layers as if already woodland and weight positively (e.g. ecosystem services potentially provided flood mitigation, water quality benefits…).  
v.	Identify facilitating factors for converting to woodland from existing landcover and weight positively (land ownership, river banks?).  
vi.	Prioritize “woodland creation opportunities” through zonation method and keep highest priority areas. Will generally value areas with multiple benefits (eg connectivity and flood mitigation benefit).    

### Excluded areas 
Many areas can be excluded a priori from any consideration for woodland creation. However some of these areas (ie existing woodland and priority habitats) are included in determining the connectivity benefits of woodland creation.  
  
```{r}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.exclude.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.exclude.df)),
          rownames=FALSE,colnames = c('Excluded Area','Inclusion','Data Source','Notes'))
```


### Constraining factors
Constraining factors are any factor likely to act as a constraint on sucessful woodland creation and the realisation of potential benefits (including the loss of benefit from other landuses). Although not entirely excluded from consideration these factors are given a negative weighting in the analysis. Such factors include  the proportion of an area that is buildings, high grade agricultural land, and topographical constraints to sucessful woodland growth.   
  
```{r}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.constrain.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.constrain.df)),
            rownames=FALSE,colnames = c('Constraint Factor', 'Inclusion','Data Source','Notes'))
```

### Facilitating factors 
Facilitating factors are factors that decrease the cost or increase the probability of realising the benefits of woodland creation and are given a positive weighting in analysis.  
  

```{r}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.facilitate.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.facilitate.df)),
  rownames=FALSE,colnames = c('Facilitating Factor', 'Inclusion','Data Source','Notes'))
```

### Potential benefits
The calculation of potential “benefits” of woodland creation were weighted positively and included potential benefits in terms of an increase in ecosystem service provision such as flood mitigation and water quality benefits.  Other factors that might be considered include the accessibility of woodland (and therefore the provision of recreation or health benefits).
  
```{r}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.benefit.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.benefit.df)),
  rownames=FALSE,colnames = c('Benefit','Calculation','Inclusion','Data Source','Notes'))
```



D. Area maps
============================================================================================

Column {.tabset}
------------------------------------------------------------------------------------------------------------

### Community Network Areas

```{r,context='data', include=FALSE}
############################################
# LOAD Parish areas
############################################


############################################
# LOAD Community network areas
############################################

# Create list of files names
cna.shp<-st_read(paste0(in.root,"community_network_areas.shp"))
st_crs(cna.shp)<-st_crs(27700)
cna.shp<-st_transform(cna.shp,4326)
cna.names<-paste0(cna.shp$NAME)
cna.names<-sort(cna.names)

cna.list<-list.files("maps/")
cna.list<-sort(cna.list)
cna.list<-paste0("maps/",cna.list)
names(cna.list)<-cna.names

```

```{r,  echo=FALSE}

bsselect(cna.list, type = "iframe")

```


### Parishes


### Catchments


### Explanatory notes
Some sort of explanation and/or legend could be placed here, perhaps including links to a methodology document etc?


