---
title: "TeviHub"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: simplex
    logo: images/SWEEPLOGO.png
---
<script>
$('.navbar-logo').wrap('<a href="http://www.sweep.ac.uk"> target=_blank');
</script>

```{r, setup, include=FALSE}
##### TO render whole site run line command:
#   rmarkdown::render_site()
#   https://jrmosedale.github.io/dashboard/

library(flexdashboard)
library(bsselectR)
library(raster)
library(leaflet)
library(magrittr)
library(colorspace)
library(rgeos)
library(ggplot2)
library(rgdal)
library(sf)
library(units)
library(leaflet.extras)
library(htmlwidgets)
library(zonator)
library(RColorBrewer)

#### iframe refs: https://stackoverflow.com/questions/15255858/set-the-iframe-height-automatically
### https://stackoverflow.com/questions/44371799/how-can-i-insert-html-widget-objects-leaflet-map-or-html-table-in-an-html-mark

################################################
# Directories
###############################################
# if (Sys.getenv("HOME")=="/Users/jm622") in.root<-paste0(Sys.getenv("HOME"),"/OneDrive - University of Exeter/Rprojects/EG4B/app/")
in.root<-"data/"
dir_cna<-paste0(in.root,"cnamaps/")
dir_ZProject<-paste0("/Volumes/Pocket_Sam/data/Zonation_Projects/Cornwall_Priority/")
dir_zinputs<-"/Volumes/Pocket_Sam/data/Zonation_data/"

################################################
# Load functions 
###############################################
source("Rscripts/functions.R")

# Presentation functions etc
csa_icons <- function() {
  awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = "green")
}

cta_icons<- function() {
  awesomeIcons(
    icon = 'ios-close',
    iconColor = 'black',
    library = 'ion',
    markerColor = "blue"
  )
}

tevi_icons <- function(tevibus){
  awesomeIcons(
    icon = tevibus$Icon,
    iconColor = 'black',
    library = 'fa',
    markerColor = tevibus$Colour
  )
}

zero_to_NA<-function(r){
  result<-calc(r,fun=function(x){ifelse(x==0,NA,x)})
  return(result)
}

# Recalculating rank after masking
rank_after_mask<-function(r,msk){
  msk.cells<-getValues(mask(r,msk))
  min.prot<-min(msk.cells,na.rm=TRUE)
  # num.prot<-length(msk.cells[-which(is.na(msk.cells))])
  rem.cells<-getValues(mask(r,msk,inverse=TRUE))
  max.rem<-max(rem.cells,na.rm=TRUE)
  new.ranks<-(rem.cells/max.rem)*1
  new.r<-setValues(r,new.ranks)
  return(new.r)
}

```

A. Business Locations and Engagement 
============================================================================================
Businesses participating (as of September 2018) in the [Tevi](https://tevi.co.uk) programme, award winners of the [Cornwall Sustainability Awards](https://www.cornwallsustainabilityawards.org) (2004-17) and [Cornwall Tourism Awards](http://www.cornwalltourismawards.org.uk) (2018 only).
Click on marker for further information.



Column {.tabset}
------------------------------------------------------------------------------------------------------------
### Map 1 Tevi Businesses

```{r,context='data', include=FALSE}

############################################
# LOAD Business data and prepare for mapping
############################################

# Business data
tevibus<- st_read(paste0(in.root,"tevibus.shp"))
csawinners<-st_read(paste(in.root,"csawinners.shp",sep=""))
cta2018<- st_read(paste0(in.root,"cta2018.shp"))
st_crs(tevibus)<-st_crs(27700)
st_crs(csawinners)<-st_crs(27700)
st_crs(cta2018)<-st_crs(27700)

```


```{r,echo=FALSE,out.width='100%', fig.align='center'}

# Create popup message
tevi.popup<-paste("<b>",tevibus$Enterprise,"</b>","<br>","Sector: ",tevibus$Sector,"<br>","Tevi Status: ",tevibus$Status,"<br>") 

teviplot<- prepare_sf_for_leaflet(tevibus)

leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addAwesomeMarkers(data=teviplot,
                    icon=tevi_icons(teviplot),  
                    label = ~as.character(Enterprise),
                    popup = tevi.popup
)


```

### Map 2 Cornwall Sustainability and Tourism Award Winners

```{r,  echo=FALSE}
# Create popup message
csa.popup<-paste("<b>",csawinners$Business,"</b>","-",csawinners$Award,csawinners$Year)
cta.popup<-paste("<b>",cta2018$Enterprise,"</b>","-",cta2018$Award,cta2018$Year)


leaflet() %>% 
setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
addProviderTiles("OpenStreetMap.Mapnik") %>%
addScaleBar() %>%
addAwesomeMarkers(data=prepare_sf_for_leaflet(csawinners),
                  icon=csa_icons(), 
                  label = ~as.character(Business),
                  popup = csa.popup,
                  group= "CSA businesses")  %>%
addAwesomeMarkers(data=prepare_sf_for_leaflet(cta2018),
                  icon=cta_icons(), 
                  label = ~as.character(Enterprise),
                  popup = cta.popup,
                  group ="CTA businesses" )  %>%
addLayersControl(
                  overlayGroups =c("CSA businesses", "CTA businesses"),
                  options = layersControlOptions(collapsed=FALSE)  
)  %>%
hideGroup(c("CTA businesses"))


```

B. Habitats & Ecosystem Services 
============================================================================================


Column {.tabset}
------------------------------------------------------------------------------------------------------------

### Map 1 Habitats

```{r,context='data', include=FALSE}

############################################
# LOAD Habitat and Service data and prepare for mapping
############################################

# Landcover data
landcover.r<-raster(paste0(in.root,"domcover.tif"))
urban.r<-calc(landcover.r,fun=function(x){ifelse(x>19,1,NA)})
arable.r<-calc(landcover.r,fun=function(x){ifelse(x==3,1,NA)})
improvgrass.r<-calc(landcover.r,fun=function(x){ifelse(x==4,1,NA)})

# Priority habitats
priority.r<-zero_to_NA(raster(paste0(in.root,"priority_habitat.tif")))

# Protected areas
#protected.r<-
#st_crs(protected.r)<-st_crs(27700)


```


```{r,  echo=FALSE}
leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addRasterImage(urban.r,color="black", 
               opacity = 0.7,project=TRUE,group="Urban") %>%
  addRasterImage(arable.r,color="brown", 
                 opacity = 0.7,project=TRUE,group="Arable") %>%
  addRasterImage(improvgrass.r,color="green", 
                 opacity = 0.7,project=TRUE,group="Improved_Grass") %>%
  addRasterImage(priority.r,color="purple", 
                 opacity = 0.7,project=TRUE,group="Priority_habitats") %>%
  # addRasterImage(protected.r,color="yellow", 
  #               opacity = 0.7,project=TRUE,group="Protected_areas") %>%
  addLayersControl(
    overlayGroups =c("Urban", "Arable","Improved_Grass","Priority_habitats","Protected_areas"),
    options = layersControlOptions(collapsed=FALSE)  ) %>%
  hideGroup(c("Arable","Improved_Grass","Priority_habitats","Protected_areas"))
```

### Map 2 Services
Key ecosystem service and associated layers are detailed below.
```{r,context='data', include=FALSE}

# Load service rasters and determine palette for each

# Soil loss mitigation
soilmitig.r<-raster(paste0(in.root,"ecoservices/ecoservice_soillossmitig_current.tif"))
crs(soilmitig.r)<- CRS('+init=EPSG:27700')
soilmitig.vals<-getValues(soilmitig.r)
soilmitig.pal<-mapcolour("soilmitig",soilmitig.vals)

# Aboveground carbon 
abovecarbon.r<-raster(paste0(in.root,"ecoservices/ecoservice_aboveground_carbon.tif"))
crs(abovecarbon.r)<- CRS('+init=EPSG:27700')
abovecarbon.vals<-getValues(abovecarbon.r)
abovecarbon.pal<-mapcolour("abovecarbon",abovecarbon.vals)

# Pollination 
pollination.r<-raster(paste0(in.root,"ecoservices/ecoservice_pollination.tif"))
crs(pollination.r)<- CRS('+init=EPSG:27700')
pollination.vals<-getValues(pollination.r)
pollination.pal<-mapcolour("abovecarbon",pollination.vals)

# Flood mitigation
floodmitig.r<-raster(paste0(in.root,"ecoservices/ecoservice_floodmitig.tif"))
crs(floodmitig.r)<- CRS('+init=EPSG:27700')
floodmitig.vals<-getValues(floodmitig.r)
floodmitig.pal<-mapcolour("floodmitig",floodmitig.vals)

# Drinking water quality
drinkqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_drinkingwater1.tif"))
crs(drinkqual.r)<- CRS('+init=EPSG:27700')
drinkqual.vals<-getValues(drinkqual.r)
drinkqual.pal<-mapcolour("drinkqual",drinkqual.vals)

# Aquaculture water quality
aquaqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_aquaculture.tif"))
crs(aquaqual.r)<- CRS('+init=EPSG:27700')
aquaqual.vals<-getValues(aquaqual.r)
aquaqual.pal<-mapcolour("aquaqual",aquaqual.vals)

# Bathing water quality 
bathqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_bathingwater.tif"))
crs(bathqual.r)<- CRS('+init=EPSG:27700')
bathqual.vals<-getValues(bathqual.r)
bathqual.pal<-mapcolour("bathqual",bathqual.vals)



```

```{r,  echo=FALSE}


leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addRasterImage(abovecarbon.r, colors=abovecarbon.pal,
               opacity = 0.8,project=TRUE, group="Aboveground_carbon") %>%
  addRasterImage(pollination.r, colors=pollination.pal,
               opacity = 0.8,project=TRUE, group="Pollination") %>%
  addRasterImage(soilmitig.r, colors=soilmitig.pal,
               opacity = 0.8,project=TRUE, group="Soil_loss_mitigation") %>%
  addRasterImage(floodmitig.r, colors=floodmitig.pal,
               opacity = 0.8,project=TRUE, group="Flood_mitigation") %>%
  addRasterImage(drinkqual.r, colors=drinkqual.pal,
               opacity = 0.8,project=TRUE, group="Drinking_water") %>%
  addRasterImage(aquaqual.r, colors=aquaqual.pal,
               opacity = 0.8,project=TRUE, group="Aquaculture") %>%
  addRasterImage(bathqual.r, colors=bathqual.pal,
               opacity = 0.8,project=TRUE, group="Bathing_water") %>%

   addLegend(position = "bottomright",
            pal=abovecarbon.pal, values=abovecarbon.vals,
            group="Aboveground_carbon", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=pollination.pal, values=pollination.vals,
            group="Pollination", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=soilmitig.pal, values=soilmitig.vals,
            group="Soil_loss_mitigation", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=floodmitig.pal, values=floodmitig.vals,
            group="Flood_mitigation", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=drinkqual.pal, values=drinkqual.vals,
            group="Drinking_water", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=aquaqual.pal, values=aquaqual.vals,
            group="Aquaculture", opacity=1) %>%
   addLegend(position = "bottomright",
            pal=bathqual.pal, values=bathqual.vals,
            group="Bathing_water", opacity=1) %>%
  
  addLayersControl(
    overlayGroups =c("Aboveground_carbon","Pollination","Soil_loss_mitigation",
                     "Flood_mitigation","Drinking_water","Aquaculture","Bathing_water"),
    options = layersControlOptions(collapsed=FALSE)  )  %>%
  
  hideGroup(c("Pollination","Soil_loss_mitigation",
             "Flood_mitigation","Drinking_water","Aquaculture","Bathing_water"))

```


### Explanatory notes
Some sort of explanation and/or legend could be placed here, perhaps including links to a methodology document etc?


C. Opportunities 
============================================================================================

Column {.tabset}
------------------------------------------------------------------------------------------------------------

### New protection areas

```{r, echo=FALSE}

opp.map1.filername<-paste0("maps/","opps/opp_nogo_map.html")

htmltools::tags$iframe(src = opp.map1.filername, frameborder="0", style="overflow: hidden; height: 100%; width: 100%; position: absolute;")
```

### Woodland creation

```{r, echo=FALSE}

opp.map1.filername<-paste0("maps/","opps/opp_woodland_map.html")

htmltools::tags$iframe(src = opp.map1.filername, frameborder="0", style="overflow: hidden; height: 100%; width: 100%; position: absolute;")
```


D. Area maps
============================================================================================

Column {.tabset}
------------------------------------------------------------------------------------------------------------

### Community Network Areas

```{r,context='data', include=FALSE}
############################################
# LOAD Parish areas
############################################


############################################
# LOAD Community network areas
############################################

# Create list of files names
cna.shp<-st_read(paste0(in.root,"community_network_areas.shp"))
st_crs(cna.shp)<-st_crs(27700)
cna.shp<-st_transform(cna.shp,4326)
cna.names<-paste0(cna.shp$NAME)
cna.names<-sort(cna.names)

cna.list<-list.files("maps/")
cna.list<-sort(cna.list)
cna.list<-paste0("maps/",cna.list)
names(cna.list)<-cna.names

```

```{r,  echo=FALSE}

bsselect(cna.list, type = "iframe")

```


### Parishes


### Catchments


### Explanatory notes
Some sort of explanation and/or legend could be placed here, perhaps including links to a methodology document etc?


