---
title: "TeviHub"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: readable
    logo: images/SWEEPLOGO.png
---
<script>
$('.navbar-logo').wrap('<a href="http://www.sweep.ac.uk"> target=_blank');
</script>

```{r, setup, include=FALSE}
##### TO render whole site run line command:
#   rmarkdown::render_site()
#   https://jrmosedale.github.io/dashboard/

# Linking multiple Rmd files - usew either bookdown or child files - reF:https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output

#  devtools::install_github("walkerke/bsselectR")

library(flexdashboard)
library(bsselectR)
library(raster)
library(leaflet)
library(magrittr)
library(colorspace)
library(rgeos)
library(ggplot2)
library(rgdal)
library(sf)
library(units)
library(leaflet.extras)
library(htmlwidgets)
library(zonator)
library(RColorBrewer)
library(DT)

#### iframe refs: https://stackoverflow.com/questions/15255858/set-the-iframe-height-automatically
### https://stackoverflow.com/questions/44371799/how-can-i-insert-html-widget-objects-leaflet-map-or-html-table-in-an-html-mark

################################################
# Directories
###############################################
# if (Sys.getenv("HOME")=="/Users/jm622") in.root<-paste0(Sys.getenv("HOME"),"/OneDrive - University of Exeter/Rprojects/EG4B/app/")
in.root<-"data/"
dir_cna<-paste0(in.root,"cnamaps/")
dir_ZProject<-paste0("/Volumes/Pocket_Sam/data/Zonation_Projects/Cornwall_Priority/")
dir_zinputs<-"/Volumes/Pocket_Sam/data/Zonation_data/"

################################################
# Load functions 
###############################################
source("Rscripts/functions.R")

# Presentation functions etc
csa_icons <- function() {
  awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = "green")
}

cta_icons<- function() {
  awesomeIcons(
    icon = 'ios-close',
    iconColor = 'black',
    library = 'ion',
    markerColor = "blue"
  )
}

tevi_icons <- function(tevibus){
  awesomeIcons(
    icon = tevibus$Icon,
    iconColor = 'black',
    library = 'fa',
    markerColor = tevibus$Colour
  )
}

zero_to_NA<-function(r){
  result<-calc(r,fun=function(x){ifelse(x==0,NA,x)})
  return(result)
}

# Recalculating rank after masking
rank_after_mask<-function(r,msk){
  msk.cells<-getValues(mask(r,msk))
  min.prot<-min(msk.cells,na.rm=TRUE)
  # num.prot<-length(msk.cells[-which(is.na(msk.cells))])
  rem.cells<-getValues(mask(r,msk,inverse=TRUE))
  max.rem<-max(rem.cells,na.rm=TRUE)
  new.ranks<-(rem.cells/max.rem)*1
  new.r<-setValues(r,new.ranks)
  return(new.r)
}

```

A. Business Locations and Engagement 
============================================================================================
Businesses participating (as of September 2018) in the [Tevi](https://tevi.co.uk) programme, award winners of the [Cornwall Sustainability Awards](https://www.cornwallsustainabilityawards.org) (2004-17) and [Cornwall Tourism Awards](http://www.cornwalltourismawards.org.uk) (2018 only).
Click on marker for further information.



Column {.tabset}
------------------------------------------------------------------------------------------------------------
### Map 1 Tevi Businesses

```{r,context='data', include=FALSE}

############################################
# LOAD Business data and prepare for mapping
############################################

# Business data
tevibus<- st_read(paste0(in.root,"tevibus.shp"))
csawinners<-st_read(paste(in.root,"csawinners.shp",sep=""))
cta2018<- st_read(paste0(in.root,"cta2018.shp"))
st_crs(tevibus)<-st_crs(27700)
st_crs(csawinners)<-st_crs(27700)
st_crs(cta2018)<-st_crs(27700)

```


```{r,echo=FALSE,out.width='100%', fig.align='center'}

# Create popup message
tevi.popup<-paste("<b>",tevibus$Enterprise,"</b>","<br>","Sector: ",tevibus$Sector,"<br>","Tevi Status: ",tevibus$Status,"<br>") 

teviplot<- prepare_sf_for_leaflet(tevibus)

leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addAwesomeMarkers(data=teviplot,
                    icon=tevi_icons(teviplot),  
                    label = ~as.character(Enterprise),
                    popup = tevi.popup
)


```

### Map 2 Cornwall Sustainability and Tourism Award Winners

```{r,  echo=FALSE}
# Create popup message
csa.popup<-paste("<b>",csawinners$Business,"</b>","-",csawinners$Award,csawinners$Year)
cta.popup<-paste("<b>",cta2018$Enterprise,"</b>","-",cta2018$Award,cta2018$Year)


leaflet() %>% 
setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
addProviderTiles("OpenStreetMap.Mapnik") %>%
addScaleBar() %>%
addAwesomeMarkers(data=prepare_sf_for_leaflet(csawinners),
                  icon=csa_icons(), 
                  label = ~as.character(Business),
                  popup = csa.popup,
                  group= "CSA businesses")  %>%
addAwesomeMarkers(data=prepare_sf_for_leaflet(cta2018),
                  icon=cta_icons(), 
                  label = ~as.character(Enterprise),
                  popup = cta.popup,
                  group ="CTA businesses" )  %>%
addLayersControl(
                  overlayGroups =c("CSA businesses", "CTA businesses"),
                  options = layersControlOptions(collapsed=FALSE)  
)  %>%
hideGroup(c("CTA businesses"))


```

B. Habitats & Ecosystem Services 
============================================================================================
Important: The habitats and estimates of key ecosystem services presented here are calculated on the basis of 2015 landcover data.


Column {.tabset}
------------------------------------------------------------------------------------------------------------
### Map 1 Habitats
```{r,context='data', include=FALSE}

############################################
# LOAD Habitat and Service data and prepare for mapping
############################################

# Landcover data
landcover.r<-raster(paste0(in.root,"domcover.tif"))
urban.r<-calc(landcover.r,fun=function(x){ifelse(x>19,1,NA)})
arable.r<-calc(landcover.r,fun=function(x){ifelse(x==3,1,NA)})
improvgrass.r<-calc(landcover.r,fun=function(x){ifelse(x==4,1,NA)})

# Priority habitats
priority.r<-zero_to_NA(raster(paste0(in.root,"priority_habitat.tif")))


```


```{r,  echo=FALSE}
leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addRasterImage(urban.r,color="black", 
               opacity = 0.7,project=TRUE,group="Urban") %>%
  addRasterImage(arable.r,color="brown", 
                 opacity = 0.7,project=TRUE,group="Arable") %>%
  addRasterImage(improvgrass.r,color="green", 
                 opacity = 0.7,project=TRUE,group="Improved Grass") %>%
  addRasterImage(priority.r,color="purple", 
                 opacity = 0.7,project=TRUE,group="Priority habitats") %>%
  # addRasterImage(protected.r,color="yellow", 
  #               opacity = 0.7,project=TRUE,group="Protected areas") %>%
  addLayersControl(
    overlayGroups =c("Urban", "Arable","Improved Grass","Priority habitats"),
    options = layersControlOptions(collapsed=FALSE)  ) %>%
  hideGroup(c("Urban","Arable","Improved_Grass","Priority_habitats"))
```

### Map 2 Services
Key ecosystem service and associated layers are detailed below.
```{r,context='data', include=FALSE}

# Load service rasters and determine palette for each

# Soil loss mitigation
soilmitig.r<-raster(paste0(in.root,"ecoservices/ecoservice_soillossmitig.tif"))
crs(soilmitig.r)<- CRS('+init=EPSG:27700')
soilmitig.vals<-getValues(soilmitig.r)

# Aboveground carbon 
abovecarbon.r<-raster(paste0(in.root,"ecoservices/ecoservice_aboveground_carbon.tif"))
crs(abovecarbon.r)<- CRS('+init=EPSG:27700')
abovecarbon.vals<-getValues(abovecarbon.r)

# Pollination 
pollination.r<-raster(paste0(in.root,"ecoservices/ecoservice_pollination.tif"))
crs(pollination.r)<- CRS('+init=EPSG:27700')
pollination.vals<-getValues(pollination.r)

# Flood mitigation
floodmitig.r<-raster(paste0(in.root,"ecoservices/ecoservice_floodmitig.tif"))
crs(floodmitig.r)<- CRS('+init=EPSG:27700')
floodmitig.vals<-getValues(floodmitig.r)

# Drinking water quality
drinkqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_drinkwater.tif"))
crs(drinkqual.r)<- CRS('+init=EPSG:27700')
drinkqual.vals<-getValues(drinkqual.r)

# Aquaculture water quality
aquaqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_aquaculture.tif"))
crs(aquaqual.r)<- CRS('+init=EPSG:27700')
aquaqual.vals<-getValues(aquaqual.r)

# Bathing water quality 
bathqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_bathingwater.tif"))
crs(bathqual.r)<- CRS('+init=EPSG:27700')
bathqual.vals<-getValues(bathqual.r)

# Not good catchments water quality 
catchqual.r<-raster(paste0(in.root,"ecoservices/ecoservice_catchmentquality.tif"))
crs(catchqual.r)<- CRS('+init=EPSG:27700')
catchqual.vals<-getValues(catchqual.r)

#servicepal<-colorBin("Greens", domain = NULL, bins = 7, na.color = "transparent")
servicepal<-colorNumeric("YlOrRd", domain = NULL,  na.color = "transparent")

```

```{r,  echo=FALSE}

leaflet() %>% 
  setView(lng = -4.9, lat = 50.4, zoom = 10)  %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addScaleBar() %>%
  addRasterImage(abovecarbon.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Aboveground_carbon") %>%
  addRasterImage(pollination.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Pollination") %>%
  addRasterImage(soilmitig.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Soil_loss_mitigation") %>%
  addRasterImage(floodmitig.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Flood_mitigation") %>%
  addRasterImage(drinkqual.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Drinking_water") %>%
  addRasterImage(aquaqual.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Aquaculture") %>%
  addRasterImage(bathqual.r, colors=servicepal,
               opacity = 0.8,project=TRUE, group="Bathing_water") %>%
  addLegend(position = "bottomright",
            pal=servicepal, values=0:100,opacity=1) %>%

  addLayersControl(
    baseGroups =c("Aboveground_carbon","Pollination","Soil_loss_mitigation",
                     "Flood_mitigation","Drinking_water","Aquaculture","Bathing_water"),
    options = layersControlOptions(collapsed=FALSE)  )  %>%
  
  hideGroup(c("Pollination","Soil_loss_mitigation",
             "Flood_mitigation","Drinking_water","Aquaculture","Bathing_water"))

```


C. Prioritization mapping 
============================================================================================
Prioritization of 'non-protected' areas according to estimates of their current biodiversity, connectivity and ecosystem services. Areas currently benefiting from SSSI, SAC, SPA, national or local natures reserves are excluded from ranking.  
The top twenty percent most highly ranked/valued areas are shown in three bands: top5%, top 5-10%, top 10-20%. Resolution = 100m2. 


Column {.tabset}
------------------------------------------------------------------------------------------------------------
### Nature network mapping

```{r, echo=FALSE}

prot.map1.filername<-paste0("maps/","opps/protect_map_vv18.html")

htmltools::tags$iframe(src = prot.map1.filername, frameborder="0", style="overflow: hidden; height: 100%; width: 100%; position: absolute;")
```

### Nature network - Method notes
```{r child = 'PRIORITYMAP_1.Rmd'}
```

   
D. Opportunity mapping 
============================================================================================
Prioritization of woodland creation opportunities on the basis of estimates of benefits associated with improved habitat area, connectivity and ecosystem services provided. Existing protected urban, woodland, quarries/claypits and protected areas are excluded from consideration, and results consider constraints affecting likely success and costs of implementation. 
The top twenty percent most highly ranked/valued oppoortunity areas are shown in three bands: top5%, top 5-10%, top 10-20%. Resolution = 100m2.


Column {.tabset}
------------------------------------------------------------------------------------------------------------

```{r,context='data', include=FALSE}
woodopp.exclude.df<-read.csv("data/documentation/woodland_exclusion_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 
woodopp.constrain.df<-read.csv("data/documentation/woodland_constraint_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 
woodopp.facilitate.df<-read.csv("data/documentation/woodland_facilitate_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 
woodopp.benefit.df<-read.csv("data/documentation/woodland_benefit_table.csv" ,header=TRUE,stringsAsFactors=FALSE, na.strings = "") 


```

### Woodland opportunity map

```{r, echo=FALSE}

opp.map1.filername<-paste0("maps/","opps/opp_woodland_map_vv09.html")

htmltools::tags$iframe(src = opp.map1.filername, frameborder="0", style="overflow: hidden; height: 100%; width: 100%; position: absolute;")

```

### Method and Approach
```{r, echo=FALSE}
#opp.map1.filername<-paste0("maps/","opps/opp_woodland_map_v08.html")
#opp.map1.filername<-paste0("maps/","opps/opp_woodland_map_v07.html")

woodopp.method<-paste0("documentation/","Woodland creation test.html")

htmltools::tags$iframe(src = woodopp.method, frameborder="0", style="overflow: hidden; height: 100%; width: 100%; position: absolute;")

```

### Excluded areas 
Many areas can be excluded a priori from any consideration for woodland creation. However some of these areas (ie existing woodland and priority habitats) are included in determining the connectivity benefits of woodland creation.  
  
```{r}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.exclude.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.exclude.df)),
          rownames=FALSE,colnames = c('Excluded Area','Inclusion','Data Source','Notes'))
```


### Constraining factors
Constraining factors are any factor likely to act as a constraint on sucessful woodland creation and the realisation of potential benefits (including the loss of benefit from other landuses). Although not entirely excluded from consideration these factors are given a negative weighting in the analysis. Such factors include  the proportion of an area that is buildings, high grade agricultural land, and topographical constraints to sucessful woodland growth.   
  
```{r}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.constrain.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.constrain.df)),
            rownames=FALSE,colnames = c('Constraint Factor', 'Inclusion','Data Source','Notes'))
```

### Facilitating factors 
Facilitating factors are factors that decrease the cost or increase the probability of realising the benefits of woodland creation and are given a positive weighting in analysis.  
  

```{r}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.facilitate.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.facilitate.df)),
  rownames=FALSE,colnames = c('Facilitating Factor', 'Inclusion','Data Source','Notes'))
```

### Potential benefits
The calculation of potential “benefits” of woodland creation were weighted positively and included potential benefits in terms of an increase in ecosystem service provision such as flood mitigation and water quality benefits.  Other factors that might be considered include the accessibility of woodland (and therefore the provision of recreation or health benefits).
  
```{r}
## DISPLAY TABLE OF DATA SOURCES
datatable(woodopp.benefit.df,options = list(dom = 't',ordering = FALSE,
          pageLength = nrow(woodopp.benefit.df)),
  rownames=FALSE,colnames = c('Benefit','Calculation','Inclusion','Data Source','Notes'))
```



D. Area maps
============================================================================================
This section is currently UNDER DEVELOPMENT

Column {.tabset}
------------------------------------------------------------------------------------------------------------

### Community Network Areas

```{r,context='data', include=FALSE}
############################################
# LOAD Parish areas
############################################


############################################
# LOAD Community network areas
############################################

# Create list of files names
cna.shp<-st_read(paste0(in.root,"community_network_areas.shp"))
st_crs(cna.shp)<-st_crs(27700)
cna.shp<-st_transform(cna.shp,4326)
cna.names<-paste0(cna.shp$NAME)
cna.names<-sort(cna.names)

cna.list<-list.files("maps/")
cna.list<-sort(cna.list)
cna.list<-paste0("maps/",cna.list)
names(cna.list)<-cna.names

```

```{r,  echo=FALSE}

bsselect(cna.list, type = "iframe")

```


### Parishes


### Catchments


### Explanatory notes
Some sort of explanation and/or legend could be placed here, perhaps including links to a methodology document etc?


